Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-02 GECCO/volunteer-clouds-gecco16.tex
Adds a paragraph at the end of the intro
To make clear what we are doing in the paper in a few sentences.
Refs #97

The rest of the paper is organized as follows: Next we present the
state of the art in web-based distributed
computational systems along with attempts to predict and model its
behavior  in Section \ref{sec:soa}. The first results in a volunteer
setting are described 
in Section \ref{sec:exp1}, and experiments using a new client
architecture that uses web workers in Section \ref{sec:w2} and then
applied to a different problem in Section \ref{sec:rastrigin}. 
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

>>>>

In this paper we will carry out three experiments, after establishing
the baseline of the performance that can be expected in a JavaScript
based system and its comparison with other languages in
\cite{2016arXiv160101607Manom}. First, several experiments using a
Platform as a Service, and a simple Ajax client that does not
restart. Second, we change a bit the client so that it uses web
workers, that is, it runs in the background and it restarts. Third, we use the same
client but with a harder problem that cannot be solved by a single
client and thus needs the contribution of many volunteers to
proceed. With these three experiments we want mainly to try and model
the behavior of users and how different problems and implementations
have an influence on it.

So, the rest of the paper is organized as follows: Next we present the
state of the art in web-based distributed
computational systems along with attempts to predict and model its
behavior  in Section \ref{sec:soa}. The first results in a volunteer
setting are described 
in Section \ref{sec:exp1}, and experiments using a new client
architecture that uses web workers in Section \ref{sec:w2} and then
applied to a different problem in Section \ref{sec:rastrigin}. 
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.
